Panel Seminars

### 2023-10-09 POP_02_RADseq.Rmd
fixing html so google scholar connects to rad page, similar to what I did for DGE the other day

```{r,message = FALSE,echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```
---
title: 'RADseq'
subtitle: '*Katherine Silliman, Danielle Davenport*'
bibliography: POP_02_RADseq_files/common-bib_01.bib
---

>>>>

---
title: 'RADseq'
subtitle: '*Katherine Silliman, Danielle Davenport*'
bibliography: POP_02_RADseq_files/common-bib_01.bib
output: 
  html_document:
    pandoc_args: [ 
      "--output=RADseq.html" 
    ]
---

```{r,message = FALSE,echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")

### 2023-10-09 index.Rmd
fixing html so google scholar connects to rad page, similar to what I did for DGE the other day

* [Choosing a population genomics sequencing approach](POP_01_choosing_population_genetics.html)  
* [Whole Genome Resequencing (WGS)](POP_04_WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](POP_02_RADseq.html) 
* [Poolseq](POP_03_poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](POP_05_RDAtraitPredictionTutorial.html)

>>>>

* [Choosing a population genomics sequencing approach](POP_01_choosing_population_genetics.html)  
* [Whole Genome Resequencing (WGS)](POP_04_WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](POP_03_poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](POP_05_RDAtraitPredictionTutorial.html)
